Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-24 paper/paper-mainfile.tex
back to cycle-break

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.

\subsection{Simple Inference of Preconditions and Effects for Compound Tasks}
For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
\begin{align*}
& \forall t \in T_P : \PreS(t) := \Pre(t) \\
& \forall t \in T_P : \AddS(t) := \Add(t) \\
& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
\end{align*}

\subsection{Complex Inference of Effects for Compound Tasks}
The work by~\cite{ConnyPreEstimation}, details a way to infer a subset of the mandatory preconditions and effects.

\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.

So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-
relaxed variant of D.

There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.

\subsection{Inference of Preconditions and Effects for Lifted Domain}
In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

@@

This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. For variant 1, only one linearized lifted method per partially-ordered lifted method is produced.

\section{Linearization Using Inferred Preconditions and Effects}
\begin{algorithm}
	\caption{Linearization using inferred set of preconditions and effects} %\caption{Calculation of linearized methods}
	\label{alg:Algorithm1}	
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
	{

		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}

		$G \gets$ calculateTransitiveClosure($\singlePrec$) \\
		\label{alg:StartBuildGraph}
		\For{a $\in$ F}{  
			\For{$t \in T_m$}{
				\For{$t' \in T_m$}{
					if $a \in \AddS(t)$ and $a \in \PreS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$  \\ 
					if $a \in \AddS(t)$ and $a \in \DelS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \PreS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \AddS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$ \\  
				}
			} 
			\label{alg:EndBuildGraph}	
		}	 
		\label{alg:TopSort}
		$\singlePrec'\gets$ any linearization of $G$ \\
		$m' = (tasks(m), \singlePrec', \alpha(t))$ \\
		$M' = M' \cup  \{m'\}$ \\		
	}
	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
\end{algorithm}

@@

\subsection{Theoretical Properties If Using Simple Inference}
\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

	The Floyd-warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,

	To calculate $\PreS, \AddS, \DelS$ for each task $t$. We explore it's compound sub-tasks until we collect all primitive tasks. Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree. This provides an upper limit of $(3 * |F| * |T_p|) + T_C$. This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$. % we explore all poss (at most $|T_C|$)

@@

@@

	So in total the main algorithm takes: \newline
	$(|M| * |T|^3)$ +          % Floyd-Warshall
	$(|M| * |F| * |T|)$  +    % GetPreEff
	$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
	$(|M| * |T|)$        % topological sort
\end{proof}

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

\begin{theorem}\label{thm:notCompleteness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then $sol(P')$ may be empty.
\end{theorem}
\begin{proof}
	This algorithm linearizes all the methods to be totally ordered. Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other. This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered. Consider the simple example problem:

	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$. This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution. 
	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.

	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete. Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
\end{proof}

@@

\subsection{Performance of Simple Linearization}

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}} 
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

\subsection{Performance of Complex Linearization}

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

\begin{table*}[h]
	\scalebox{1} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{  \rotatebox{80}{rc2(Add)}} & 
			\multicolumn{2}{c}{   \rotatebox{80}{rc2(Filter)}} & 
			\multicolumn{2}{c}{  \rotatebox{80}{rc2(FF)}}
			& \multicolumn{2}{c}{   \rotatebox{80}{rc2(LMC)}}  
			& \multicolumn{2}{c}{  \rotatebox{80}{HTN2SAS}}
& \multicolumn{2}{c}{  \rotatebox{80}{HyperTensioN}}
& \multicolumn{2}{c}{  \rotatebox{80}{Lilotane}} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table*}

>>>>

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.

\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

@@

This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. Only one linearized lifted method per partially-ordered lifted method is produced.

For a grounded method, there are no parameters in a task or method. Methods decompose to specific actions, actions have preconditions and effects on specific state variables. We can then use these to produce a linearized grounded method per grounded method.

In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
\begin{align*}
& \forall t \in T_P : \PreS(t) := \Pre(t) \\
& \forall t \in T_P : \AddS(t) := \Add(t) \\
& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
\end{align*}

\subsection{Complex Inference of Effects for Compound Tasks (for Grounded Domain) }
The work by~\cite{ConnyPreEstimation}, details a way to infer a subset of the mandatory preconditions and effects.

\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.

So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.

There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
In this paper, we will be utilizing the precondition-relaxed possible effects, which guaranteed to hold after at least one refinement of c.

%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
%f ∈ prec(ai) and there does not exist an action aj with
%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
%The exploitation of the relaxed preconditions and effects
%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates

\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}

\begin{algorithm}[h]
	\caption{Calculation of linearized methods}
	\label{alg:Algorithm1}
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
	{
		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
		$G \gets \singlePrec$ \\
		\label{alg:StartBuildGraph}
		\For{a $\in$ F}{  
			\For{$t \in T_m$}{
				\For{$t' \in T_m$}{
					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
				}
			} 
			\label{alg:EndBuildGraph}	
		}	
		\label{alg:StartCycleBreak}
		\While{$G$ has cycles in it}{
			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
		}
		\label{alg:EndCycleBreak}
		$\prec'$ = Any linearization of $G$ \\
		\label{alg:TopSort}
		$m' = (tasks(m), \prec', \alpha(t))$ \\
		$M' = M' \cup  \{m'\}$ \\

	}
	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
\end{algorithm}

@@

\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,

	To calculate $\PreS, \AddS, \DelS$ for each task $t$. We explore it's compound sub-tasks until we collect all primitive tasks. Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree. This is obviously polynomial in terms of $|T|$. %This provides an upper limit of $(3 * |F| * |T_p|) + T_C$. This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$. % we explore all poss (at most $|T_C|$)

@@

	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.

@@

	So the algorithm takes polynomial time.
	%So in total the main algorithm takes: \newline
	%$(|M| * |T|^3)$ +          % Floyd-Warshall
	%$(|M| * |F| * |T|)$  +    % GetPreEff
	%$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
	%$(|M| * |T|)$        % topological sort
\end{proof}

\subsection{Theoretical Properties If Using Simple Inference (for Grounded Or Lifted)}
\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

\begin{theorem}\label{thm:notCompleteness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then $sol(P')$ may be empty.
\end{theorem}
\begin{proof}
	This algorithm linearizes all the methods to be totally ordered. Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other. This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered. Consider the simple example problem:
	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$. This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution. 
	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete. Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
\end{proof}

@@

\begin{table*}[h]
	\centering
	\subcaption{Coverage achieved, using Simple Inference on Grounded (Linearized) Problem}
	\scalebox{1} {
	\begin{tabular}{lccccccccccccccccl} 
	\toprule 
	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
	\midrule 
	Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{9.0}  } \\ 
	Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & 15.0 &\multicolumn{2}{c}{ \textbf{16.0}  } \\ 
	Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & 14.0 & \textbf{15.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
	PCP$^{17}$ & 17 & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
	Rover & 20 & 6.0 & \textbf{20.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{19.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
	Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\  
	Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{12.0}  } \\ 
	UM-Translog$^{1}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ \textbf{22.0}  } \\ 
	Woodworking$^{2}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{15.0} & 12.0 & \textbf{20.0} & 9.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
	\midrule 
	Monroe & 100 & 96.0 & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
	SmartPhone$^{1}$ & 7 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
	Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
	\midrule 
	Coverage & 335 & 239.0 & \textbf{287.0} & 188.0 & \textbf{232.0} & 231.0 & \textbf{274.0} & 198.0 &\multicolumn{2}{c}{ \textbf{237.0}  } \\ 
	Norm. coverage & 12 & 8.22 & \textbf{9.95} & 6.85 & \textbf{8.46} & 8.0 & \textbf{9.63} & 7.1 &\multicolumn{2}{c}{ \textbf{8.44}  } \\ 
	\bottomrule 
	\end{tabular}
	}
\end{table*}

		%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

\begin{table*}[h]
	\centering
	\caption{IPC score achieved, using Simple Inference, on Grounded Problems}
	\scalebox{1} {
\begin{tabular}{lccccccccccccccccl} 
	\toprule 
	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
	\midrule 
	Barman-BDI & 1 & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
	Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.56} & 0.45 & \textbf{0.31} & 0.3 & \textbf{0.46} & 0.41 & \textbf{0.22} &\multicolumn{2}{c}{ 0.18  } \\ 
	Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} & 0.25 & \textbf{0.13} & 0.11 & \textbf{0.31} & 0.26 & \textbf{0.17} &\multicolumn{2}{c}{ 0.14  } \\ 
	PCP$^{17}$ & 1 & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ \textbf{0.82}  } \\ 
	Rover & 1 & 0.29 & \textbf{0.95} & 0.14 & \textbf{0.52} & 0.2 & \textbf{0.78} & 0.16 &\multicolumn{2}{c}{ \textbf{0.48}  } \\ 
	Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
	Transport & 1 & 0.24 & \textbf{0.61} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 &\multicolumn{2}{c}{ \textbf{0.2}  } \\ 
	UM-Translog$^{1}$ & 1 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
	Woodworking$^{2}$ & 1 & 0.38 & \textbf{0.58} & 0.2 & \textbf{0.41} & 0.36 & \textbf{0.57} & 0.27 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
	\midrule 
	Monroe & 1 & \textbf{0.77} & 0.69 & \textbf{0.5} & 0.47 & \textbf{0.75} & 0.71 & \textbf{0.53} &\multicolumn{2}{c}{ \textbf{0.53}  } \\ 
	SmartPhone$^{1}$ & 1 & \textbf{0.71} & \textbf{0.71} & 0.69 & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} &\multicolumn{2}{c}{ \textbf{0.71}  } \\ 
	Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
	\midrule 
	IPC score & 12 & 7.1 & \textbf{8.4} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.9} & 5.8 &\multicolumn{2}{c}{ \textbf{6.7}  } \\
	\bottomrule 
\end{tabular} 
	}
\end{table*}
